### 2024-01-14 nondirectional_ms_2024.Rmd
Add a zipped file of the results
small text correction

source('datasets_analysis\\utils.R')
source('datasets_analysis\\definitions.R')
```

@@

To examine whether lack of power can explain not finding convincing evidence for non-directional unconscious processing effects (Fig. 3), we examined the sensitivity of the sign-consistency test in detecting effects of empirically relevant studies.
To that end, we simulated *non-directional differences* scenarios with different degrees of true between participants variance ($\sigma_b \in \{1, 1.5, 2\}$) and fixed amount of within participant variability ($\sigma_w = 10$). These parameters were chosen based on previous works where the ratio $\frac{\sigma_b}{\sigma_w}$ was estimated to values ranging between .04 and .15 (M = .1, SD = .04) in six unconscious processing datasets [@meyen2022a], while in another work estimating the same parameter in 24 cognitive control studies [@rouder2023a] (where no unconscious manipulation was used) values ranged between .05 and .36 (M = .14, SD = .08). Then, we determined the number of trials and participants in the simulated datasets according to the parameters used in the unconscious processing datasets we obtained by calculating the 25%, 50%, and 75% percentile of both parameters. This resulted in additional simulation conditions where the number of participants was set to $N_p \in \{`r apndxF_N_p[1]`, `r apndxF_N_p[2]`, `r apndxF_N_p[3]`\}$ and the total number of trials was set to $N_t \in \{`r apndxF_N_t[1]`, `r apndxF_N_t[2]`, `r apndxF_N_t[3]`\}$. All other simulation parameters were the same as detailed in Appendix B.

>>>>

source('datasets_analysis\\utils.R')
source('datasets_analysis\\definitions.R')

# extract the datasets results from the zipped results file
unzip('results\\results.zip', exdir = 'results\\')
```

@@

To examine whether lack of power can explain not finding convincing evidence for non-directional unconscious processing effects (Fig. 3), we examined the sensitivity of the sign-consistency test in detecting effects of empirically relevant studies.
To that end, we simulated *non-directional differences* scenarios with different degrees of true between participants variance ($\sigma_b \in \{1, 1.5, 2\}$) and fixed amount of within participant variability ($\sigma_w = 10$). These parameters were chosen based on previous works where the ratio $\frac{\sigma_b}{\sigma_w}$ was estimated to values ranging between .04 and .15 (M = .1, SD = .04) in six unconscious processing datasets [@meyen2022a], while in another work estimating the same parameter in 24 cognitive control studies [@rouder2023a] (where no unconscious manipulation was used) values ranged between .05 and .36 (M = .14, SD = .08). Then, we determined the number of trials and participants in the simulated datasets according to the parameters used in the unconscious processing datasets we obtained by calculating the 25%, 50%, and 75% percentile of both parameters. This resulted in additional simulation conditions where the number of participants was set to $N_p \in \{`r apndxF_N_p[1]`, `r apndxF_N_p[2]`, `r apndxF_N_p[3]`\}$ and the total number of trials was set to $N_t \in \{`r apndxF_N_t[1]`, `r apndxF_N_t[2]`, `r apndxF_N_t[3]`\}$. All other simulation parameters were the same as detailed in Appendix C.
